---
title: "Agri Production in India"
output: html_document
---
#Introduction :
India's agriculture is composed of many crops, with the foremost food staples being rice and wheat.  
Indian farmers also grow pulses, potatoes, sugarcane, oilseeds, and such non-food items as cotton, tea, coffee, rubber, and jute.  
Despite the overwhelming size of the agricultural sector, however, yields per hectare of crops in India are generally low compared to international standards.  
Improper water management is another problem affecting India's agriculture.  
At a time of increasing water shortages and environmental crises, for example, the rice crop in India is allocated disproportionately high amounts of water.  
It is estimated that as much as one-fifth of the total agricultural output is lost due to inefficiencies in harvesting, transport, and storage of government-subsidized crops.

So lets us analyse more about the crop cultivation, cost invested, seasons for cultivation.  
Have used **Lattice** package for Visualization.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressMessages(library(lattice))
suppressMessages(library(dplyr))
suppressMessages(library("latticeExtra"))
suppressMessages(library(gridExtra))
suppressMessages(library(tidyr))
suppressMessages(library(RColorBrewer))
```
  
Exists 5 source files , which has details about crop varierties, crop production, cost cost etc. Let us analyse the file one by one.  
```{r}
setwd("../input/")
produce<-read.csv("produce.csv")
crop<-read.csv("datafile.csv")
crop_var<-read.csv("datafile (3).csv")
crop_prod<-read.csv("datafile (2).csv")
crop_cost<-read.csv("datafile (1).csv")
```
  
###1) Crop Variety  
```{r}
str(crop_var)
head(crop_var)
```
  
###2) Crop Cultivation and Yeild Cost  
Glimpse of data  
```{r}
str(crop_cost)
head(crop_cost)
``` 
Total Yeild for crops  .. Which crop Yeilds more in India?   

```{r echo=FALSE}

yeild<-crop_cost %>% select(Crop,Yield..Quintal..Hectare..)%>% group_by(Crop)%>% summarise(yeild=sum(Yield..Quintal..Hectare..))
yeild
barchart(yeild~Crop, data=yeild,xlab = "crop",
auto.key = list(adj = 1),
scales=list (x=list(cex=0.8, rot=90)),fill="blue",col="blue")
```
  
What is the cost of Production(Quintal) for crops?  
```{r echo=FALSE}
histogram(~Cost.of.Production....Quintal..C2|Crop ,data=crop_cost,col="navyblue")
```
  
What is the cost of Cultivation(Hectare) for crops?  
```{r echo=FALSE}
bwplot(Cost.of.Cultivation....Hectare..C2 ~ State |Crop, data = crop_cost,
varwidth = TRUE,
ylab = "Cost of Cultivation/Hectare",
xlab="Crop",
col="red",cex.label=1,fill="blue",main="Cost of Crop cultivation per Hectare",
scales=list (x=list(cex=0.8, rot=90)),
layout=c(2,2))
```
  
Major Crops yeilds - Major Contributors  
```{r echo=FALSE}
cc<-crop_cost %>% select(Crop,State,Yield..Quintal..Hectare..)%>% filter(Crop=="SUGARCANE")%>% mutate(Total= sum(Yield..Quintal..Hectare..),percent=(Yield..Quintal..Hectare../Total)*100)

g1<-barchart(percent ~ State,data=cc,fill="grey",col="grey50",main="Statewise Sugarcane Yeild")

cot<-crop_cost %>% select(Crop,State,Yield..Quintal..Hectare..)%>% filter(Crop=="COTTON")%>% mutate(Total= sum(Yield..Quintal..Hectare..),percent=(Yield..Quintal..Hectare../Total)*100)
g2<-barchart(percent ~ State,data=cot,fill="green4",col="green4",main="Statewise COTTON Yeild")

pad<-crop_cost %>% select(Crop,State,Yield..Quintal..Hectare..)%>% filter(Crop=="PADDY")%>% mutate(Total= sum(Yield..Quintal..Hectare..),percent=(Yield..Quintal..Hectare../Total)*100)
g3<-barchart(percent ~ State,data=pad,fill="red4",col="red4",main="Statewise PADDY Yeild")
wh<-crop_cost %>% select(Crop,State,Yield..Quintal..Hectare..)%>% filter(Crop=="WHEAT")%>% mutate(Total= sum(Yield..Quintal..Hectare..),percent=(Yield..Quintal..Hectare../Total)*100)
g4<-barchart(percent ~ State,data=wh,fill="blue",col="blue",main="Statewise WHEAT Yeild")
grid.arrange(g1,g2,g3,g4,nrow=2,ncol=2)
```

3)Crops

```{r}
str(crop)
head(crop)
```
  
This dataset has year columns as rows, so lets convert it with tidyr- gather().
```{r}
crop1<-gather(crop,"Year","Value",X2004.05:X2011.12)
head(crop1)
```

```{r}

colors <- brewer.pal(n = nlevels(crop1$Crop), name = "Set1")
crop1$Value[is.na(crop1$Value)]<-0
crop1$Year<-as.factor(crop1$Year)

xyplot(Value ~ Year,group=Crop,
data = crop1, lty = 1, col = colors,ylab = "Y",
type = c("l"), distribute.type = TRUE,
key = list(text = list(levels(crop1$Crop)),
lines = TRUE, space = "bottom",col=colors))
```